ONE ARABESQUE IN THE SMALL WORLD OF OD WEBMAPS

### 2021-07-29 presentations/FOSS4G2021_presentation.Rmd
Complete structure

---
title: "ONE ARABESQUE IN THE SMALL WORLD OF OD WEBMAPS"
subtitle: "FOSS4G 2021"  
author: 
  - "Nicolas Roelandt"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#2f2a85",
  secondary_color = "#2f2a85",
  inverse_header_color = "#ef7d00"
)
```
class: inverse center middle

<style>
.top_left {
    left: 0;
    position: absolute;
    top: 0;
}
.top_left img {
margin: 0;
}

.top_right {
    right: 0;
    position: absolute;
    top: 0;
}
.top_right img {
margin: 0;
}
</style>

@@

@@

toto
---
layout: false
class: center, middle

>>>>

---
title: "ONE ARABESQUE IN THE SMALL WORLD OF OD WEBMAPS"
subtitle: "FOSS4G 2021"  
author: 
  - "Nicolas Roelandt"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    seal: false
    css: ["xaringan-themer.css", "custom.css"]
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#2f2a85",
  secondary_color = "#2f2a85",
  inverse_header_color = "#ef7d00"
)
```

class: inverse center middle title-slide

@@

---
Applications similar to Arabesque :
  * Web applications
  * FOSS
  * OD data visualisation capabilities

Opportunities for action on the data and their representation, export, etc. 
Types of cartographic rendering
---
layout: false
class: inverse center middle
# Data model

---
layout: true
# Data model
---

* data format may varie

--
* data stockage may varie : wide/large matrix format

--
* nodes coordinates in WGS84 (lat/lon)

--
* no cleaning tools provided

???
Data format: 2 files nodes / links is the most common (all but Kepler.gl).
Cleaning:
Your data needs to be prepared ahead using other tools.
Arabesque provide information on rejected data.

---
layout: false
class: inverse center middle
# Usage

---
layout: true
# Usage
---
* Data Analysis
  * Arabesque only

--
* Exploration
  * Arabesque
  * KeplerGL
  * Flowmap.blue

???
Only Arabesque offers real data analysis capabilities with custom filtering options and new indicators computation.

@@

* Representation
  * Arabesque
  * KeplerGL
  * Flowmap.blue
  * Magrit

???
All applications can be used to represent OD data.
However Kepler.gl and Flowmap.blue offers limited design options (3D arcs).
Magrit is dedicated to thematic mapping

---
layout: false
class: inverse center middle
# Public/Purpose

---
layout: true
# Public/Purpose
---

* Data exploration and visualisation
    * data journalist
    * general public
    * web publishing

* Academia and teaching
    * thematic maps production
    * statistical analysis capabilities
    * Arabesque and Magrit

---
layout: false
class: inverse center middle
# Performance

---
layout: true
# Performance
---

* Technology dependant
  * KeplerGl and Flowmap.blue
    * Deck.gl
    * large datasets
    * fast
    * limited graphic options
  * Arabesque and Magrit
    * D3
    * smaller datasets (< 10 000 objects)
    * more graphic options

---
layout: false
class: inverse center middle
# Interoperability and reproducibility

---
layout: true
# Interoperability and reproducibility
---

## data format

  * CSV and/or GeoJSON
  * 2 separates tables (except for KeplerGL)
  * for Arabesque, Magrit and Flowmap.blue, you can use the same files
      * note that for Flowmap.blue you will have to save the CSV file in a google sheet document or copy-paste the data in a browser

---
## Export

  • online hosting (KeplerGL, Flowmap.blue)
  • image export (Arabesque, Magrit)
  • Data and project parameters (Arabesque, KeplerGl, Magrit)

---
layout: false
class: inverse center middle
# Conclusion

---
layout: true
# Conclusion
---  
# Conclusion

- business culture, user's skills and final use of the map influence the choice of the tool because it will influence the chosen approaches (exploration and/or analysis)
- data does not influence the choice of the tool
- whole range of needs and possibilities are covered, for the benefits of the community.
layout: false
class: center, middle
